Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive PD diagnosis for GLAD/EDGI prepan

GLAD.prepan_PD_positive <- GLAD.prepan %>%
  select(personality) %>% 
  filter(psychotic_disorders_numeric == 1)

>>>>

GLAD.prepan_PD_positive <- GLAD.prepan %>%
  select(personality_disorder_numeric) %>% 
  filter(personality_disorder_numeric == 1)

GLAD.prepan_PD_positive <- GLAD.prepan_PD_positive %>% 
  summarise("Personality disorders" = n())
